---
title: "Project"
author: "Alexa Kraklau, Sara Knight"
date: "2/28/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Our topic is based from a previous Tidy Tuesday data set of all Scooby Doo television show episodes and movies. https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-13/readme.md For each observation there are many variables including the monster, the person under the mask, the member who unmasked them, etc. Since neither one of us has a lot of R experience, we thought this would be a good data set to look at because it has several quanitative and categorical variables that we are able to analyse.

We plan to create graphical displays of certain variables to identify the efficacy of Mystery Inc as well as the individual members. There are also other directions we could go such as mapping locations or generating episode combinations.

```{r scoobydoo}
scoobydoo <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-13/scoobydoo.csv')
```

```{r ggplot2}
library(ggplot2)
```

```{r bar graph}

ggplot(data=scoobydoo, aes(x=monster_real, fill=monster_real)) +
    geom_bar(colour="black", stat="Count") +
    guides(fill=FALSE)

```
```{r bar graph #2}

ggplot(data=scoobydoo, aes(x=arrested, fill=arrested)) +
    geom_bar(colour="black", stat="Count") +
    guides(fill=FALSE)


```
